# This is the data from an experiment. The IV is the experimenal condition with 4 levels. Its moderator is General Conspiracy Belief. The DV will be changed in each graph.

```{r}
library(tidyverse)
library(gghighlight)
library(here)
```

```{r}
data <- read.csv(here("data.csv"))
```

# Create Plot 1: DV is Intention to vaccinate their fictional children.
# P.S. I cannot rename one of my variables: from "ï..GenConBlf" into "GenConBlf". If you could, please let me know.
#Weird, it comes across correctly for me, so I just changed the lines in question.
#Strengths: The color scheme for this first visualization is really pleasing to me. The range of colors goes together nicely, and it looks like it might be reasonably colorblind friendly as well.
#Possible improvement: I would like to know more about how the Y-axis is quantified.


```{r}
data %>% ggplot(aes(GenConBlf, VacIntMMR))+
  geom_point(aes(color = Condition), alpha = .3)+
  geom_smooth(aes(color = Condition), method = "lm", se = FALSE)+
  labs(title = "Do parents with conspiracy beliefs intend to vaccinate their child?",
       subtitle = "An experiment of different message types",
       x = "MMR vaccination intention",
       y = "Level of general conspiracy belief")+
  scale_color_manual(values = c("orchid", "salmon", "darkturquoise", "chartreuse3"),
                     name = "Message Type", 
                     breaks =  c("Control", "Fact", "Narrative", "Hybrid"),
                     labels = c("No exposure", "Scientific Fact", "Narrative", "Hybrid"))+
  theme_minimal()
  
```

#Let's look at each condition separately. I might create an animation at the end.
#This graph is for Control Condition.

#Again, great color use...just a really clean look.
# Only suggestion I might have would be to use a caption or subtitle to let the audience know what they are looking at in this particular visualization.
```{r}
data %>% 
  ggplot(aes(GenConBlf, VacIntMMR))+
  geom_point(color = "grey80")+
  geom_point(data = filter(data, Condition == "Control"), color = "orchid")+
  geom_smooth(data = subset(data, Condition == "Control"), method = "lm", color = "orchid", se = FALSE)+
  labs(title = "Do parents with conspiracy beliefs intend to vaccinate their child?",
       subtitle = "Vaccination Intention With No Message Exposure",
       x = "MMR vaccination intention",
       y = "Level of general conspiracy belief")+
  theme_minimal()
```

# This graph is for Fact Condition
#It might be my lack of knowledge on the subject but I think I would like to know more about what the different conditions indicate.
```{r}
data %>% 
  ggplot(aes(GenConBlf, VacIntMMR))+
  geom_point(color = "grey80")+
  geom_point(data = filter(data, Condition == "Fact"), color = "salmon")+
  geom_smooth(data = subset(data, Condition == "Fact"), method = "lm", color = "salmon", se = FALSE)+
  labs(title = "Do parents with conspiracy beliefs intend to vaccinate their child?",
       subtitle = "An experiment of different message types",
       x = "MMR vaccination intention",
       y = "Level of general conspiracy belief")+
  theme_minimal()
```

#This graph is for Narrative Condition
```{r}
data %>% 
  ggplot(aes(GenConBlf, VacIntMMR))+
  geom_point(color = "grey80")+
  geom_point(data = filter(data, Condition == "Narrative"), color = "darkturquoise")+
  geom_smooth(data = subset(data, Condition == "Narrative"), method = "lm", color = "darkturquoise", se = FALSE)+
  labs(title = "Do parents with conspiracy beliefs intend to vaccinate their child?",
       subtitle = "An experiment of different message types",
       x = "MMR vaccination intention",
       y = "Level of general conspiracy belief")+
  theme_minimal()
  
```
# This graph is for Hybrid Condition
```{r}
data %>% 
  ggplot(aes(GenConBlf, VacIntMMR))+
  geom_point(color = "grey80")+
  geom_point(data = filter(data, Condition == "Hybrid"), color = "chartreuse3")+
  geom_smooth(data = subset(data, Condition == "Hybrid"), method = "lm", color = "chartreuse3", se = FALSE)+
  labs(title = "Do parents with conspiracy belief intent to vaccinate their child?",
       subtitle = "An experiment of different message types",
       x = "MMR vaccination intention",
       y = "Level of general conspiracy belief")+
  theme_minimal()
  
```


#Create Plot 2: This graph shows means of General Conspiracy Belief of each age group according to their self-identify political ideology.

```{r}
data <- data %>% group_by(SlfPolIdeo, age) %>% 
  mutate(avg_GenCon = mean(GenConBlf, na.rm = TRUE)) %>% 
  ungroup()
```

#OK, this one I mixed the colors up a little as it didn't seem as color-blind friendly...but I don't love the result. Your other visualizations are easier on the eyes than mine here, so maybe use your eye for aesthetics  to make it colorblind friendly and as smooth as the previous visualizations? I did try to keep the general Blue/Red thing in mind for the major parties, but what color are independents?
#Is there an odd gap in the data? I don't see any young democrats or old independents.
#Did \n give you a break in your legend? If so that's pretty cool!

```{r}
data %>% filter(age != " ") %>% 
  filter(SlfPolIdeo != "Other:") %>% 
  ggplot(aes(age, avg_GenCon))+
  geom_col(aes(fill = SlfPolIdeo), position = "dodge")+
  labs(title = "Conspiracy belief in general of participants across age and political party",
       x = "Age groups",
       y = "Average conspiracy belief in general")+
  scale_fill_manual(values = c("#00B7E9", "#242424", "#FC6426"),
                     name = "Self-identified \npolitical party", 
                     breaks =  c("Democrats", "Independents", "Republicans"),
                     labels = c("Democrats", "Independents", "Republicans"))+
  theme_minimal()
```

#Plot 3: I might want to create an animation showing that, compared to conspiracy beliefs in general, conspiracy belief likely higher among the same group of population.

```{r}
data$PolIdeo <- data$PolIdeo %>% factor(c("Very conservative", "Conservative", "Neither liberal nor conservative", "Liberal", "Very liberal"))
data$Edu <- data$Edu %>% 
  factor(c(levels = "High school degree or equivalent (e.g. GED)", "Some college, no degree", "Associate degree (e.g. AA, AS)", "Bachelor's degree (e.g. BA, BS)", "Master's degree (e.g., MA, MS, MEd)"))
```

```{r}
data$Edu <- recode_factor(data$Edu, "High school degree or equivalent (e.g. GED)" = "High school degree", "Some college, no degree" = "Some College, no degree", "Associate degree (e.g. AA, AS)" = "Associate's degree", "Bachelor's degree (e.g. BA, BS)" = "Bachelor's degree", "Master's degree (e.g., MA, MS, MEd)" = "Master's degree")
```

#Again, really visually pleasing option for the heat map, and it gets the information across very nicely. Good effort on the x-axis label tilting.
#Seems like Associate's degrees might produce conspiracy theorists...or maybe that's just what they want you to think?
```{r}
data %>% filter(Edu != "NA") %>%  
  ggplot(aes(x = PolIdeo, y = Edu))+
  geom_tile(aes(fill = GenConBlf), color = "white")+
  scale_fill_viridis_c(option = "magma")+
  labs(title = "Conspiracy belief in general of participants across political ideology and education",
       x = "Political ideology",
       y = "Degree of education",
       fill = "General\nconspiracy\nbelief level")+
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.65),
    axis.text.x = element_text(angle = 25, hjust = 1))
```
```{r}
data %>% filter(Edu != "NA") %>%  
  ggplot(aes(x = PolIdeo, y = Edu))+
  geom_tile(aes(fill = VacConBlf), color = "white")+
  scale_fill_viridis_c(option = "magma")+
  labs(title = "Conspiracy belief in vaccination of participants across political ideology and education",
       x = "Political ideology",
       y = "Degree of education",
       fill = "Vaccination\nconspiracy\nbelief level")+
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.60),
    axis.text.x = element_text(angle = 25, hjust = 1))
```

#Plot 4:
```{r}
data %>% filter(Gender == c("Female", "Male")) %>% 
  ggplot(aes(GenConBlf)) +
  geom_density(aes(fill = Gender), color = "white", alpha = .3)+
  labs(title = "Males vs Females: Who has higher general conspiracy belief?",
       x = "Level of general conspiracy belief",
       y = "This viz makes me wonder what thy Y represents here")+
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
data %>% filter(Gender == c("Female", "Male")) %>% 
  ggplot(aes(VacConBlf)) +
  geom_density(aes(fill = Gender), color = "white", alpha = .3)+
  labs(title = "Males vs Females: Who has higher vaccination conspiracy belief?",
       x = "Level of vaccination conspiracy belief",
       y = "This one, too")+
  theme_minimal()+
  theme(plot.title = element_text(hjust = 0.5))
```



